Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
RL

\subsection{Supervised learning on image data sets}

@@

In this section, we show that \our's uncertainty estimates can be used to guide exploration in model-based RL;
demonstrating the quality of our uncertainty estimates.
% Uncertainty-guided decision making strategies
We test \our by using it to learn a dynamics model within a model-based RL strategy which uses posterior sampling to guide exploration
\cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
We use the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
The goal is to swing the pole up and balance it around the upward position.
We increase the difficulty of exploration by using a sparse reward function.
We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithim we implement and our experiment's configuration.

\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neural
networks (green) and a basic MLP wih no uncertainty (magenta).
To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
% that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
The training curves show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes, i.e.
it is more sample efficient.
As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.

@@

 \todo{I'm thinking we should take out the SFR with updates result}
\begin{figure}[!t]
 \centering
 \begin{subfigure}[c]{.24\textwidth}
 \resizebox{\textwidth}{!}{%
 \begin{tikzpicture}[inner sep=0,outer sep=0]

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
 \begin{subfigure}[c]{.74\textwidth}
   \centering\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.5\figurewidth}
   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Cartpole swingup with sparse reward} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and DDPG, the model-free baseline (yellow).}
 \label{fig:rl}
\end{figure}

>>>>

\subsection{Supervised learning on image data sets}
\label{sec:image}

@@

% Make custom TikZ command (argument: colour)
\newcommand{\lab}[1]{\tikz[baseline=-.8ex]{\node[minimum width=2em,minimum height=.8em,fill=#1,opacity=.1](a){};\draw[#1,thick](a.west)--(a.east);}}

% The methods
\definecolor{darkgray176}{RGB}{176,176,176} % darkgray176
\definecolor{color-our}{RGB}{0,191,191} %darkturquoise0191191
\definecolor{color-mlp}{RGB}{191,0,191} % darkviolet1910191
\definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
\definecolor{green01270}{RGB}{0,127,0} % green01270
\definecolor{lightgray204}{RGB}{204,204,204} % lightgray204

As a final experiment, we demonstrate the capability of \our to use its uncertainty estimates as guidance for exploration in model-based reinforcement learning (RL); this serves as a practical test to the quality of our uncertainty estimates. We use \our to help learn a dynamics model within a model-based RL strategy that employs posterior sampling to guide exploration \cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
%
We use the cartpole swingup task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control (see \cref{fig:rl}).
The goal is to swing the pole up and balance it around the upward position.
We increase the difficulty of exploration by using a sparse reward function.
See \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithm, and the experiment setup.

\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neural
networks (green) and a basic MLP wih no uncertainty (magenta).
To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
The training curves show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes, i.e.
it is more sample efficient.
As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(\lab{color-our}), (\lab{color-mlp}),

@@

\begin{figure}[!t]
 \centering\scriptsize
 \begin{subfigure}[c]{.24\textwidth}
 \centering
 \textbf{Cartpole swingup setup}\\[1em]
 \resizebox{\textwidth}{!}{%
 \begin{tikzpicture}[inner sep=0,outer sep=0]

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
 \begin{subfigure}[c]{.74\textwidth}
   \raggedleft\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.5\figurewidth}
   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Cartpole swingup with sparse reward} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and DDPG, the model-free baseline (yellow).}
 \label{fig:rl}
\end{figure}
